SST_patterns

### 2019-12-16 SST_patterns.Rmd
fixed error

```{r}
# # These following three objects (MUR, OISST, CMC) need to be the complete set of lon/lat values for your satellite data
# MUR <- MUR %>%
#   select(lon, lat) %>%
#   mutate(product = "MUR")
# 
# # Decided to work with OISST and CMC as both has a time series of 30years
OISST_prod <- OISST %>%
  select(lon, lat) %>%
  unique() %>%
  mutate(product = "OISST")
# 
CMC_prod <- CMC %>%
  select(lon, lat) %>%
  unique() %>%
  mutate(product = "CMC")
# 
sat_data <- rbind(CMC_prod, OISST_prod) %>% 
#   #rbind(., CMC) %>% 
select(product, lon, lat)
# 
sat_pixels <- sat_data %>%
select(product, lon, lat) %>%
unique()
# 
# ## For testing the nest/map pipeline
# # df <- site_pixels %>%
# #   filter(site == "Lamberts Bay") %>%
# #   select(-site)
# 
match_func <- function(df){
  df <- df %>%
    dplyr::rename(lon_site = lon, lat_site = lat)
  OISST_index <- OISST_prod[as.vector(knnx.index(as.matrix(OISST_prod[,c("lon", "lat")]),
                                                 as.matrix(df[,c("lon_site", "lat_site")]), k = 1)),] %>%
    cbind(., df)
  CMC_index <- CMC_prod[as.vector(knnx.index(as.matrix(CMC_prod[,c("lon", "lat")]),
                                             as.matrix(df[,c("lon_site", "lat_site")]), k = 1)),] %>%
    cbind(., df)
  res <- rbind(OISST_index, CMC_index)
  return(res)
}
# 
# # Find the nearest pixels to each spot along the transect
# # NB: SOme pixels are used more thanonce in a transect as the spacing isn't quite larger enough between transect
# # points to not fall inside of the same 25 KM pixel
pixel_match <- site_pixels %>%
  group_by(site) %>%
  group_modify(~match_func(.x))

>>>>

```{r}
# # These following three objects (MUR, OISST, CMC) need to be the complete set of lon/lat values for your satellite data
# MUR <- MUR %>%
#   select(lon, lat) %>%
#   mutate(product = "MUR")
# 
# # Decided to work with OISST and CMC as both has a time series of 30years
OISST_prod <- OISST %>%
  select(lon, lat) %>%
  unique() %>%
  mutate(product = "OISST")
# 
CMC_prod <- CMC %>%
  select(lon, lat) %>%
  unique() %>%
  mutate(product = "CMC")
# 
sat_data <- rbind(CMC_prod, OISST_prod) %>% 
#   #rbind(., CMC) %>% 
select(product, lon, lat)
# 
sat_pixels <- sat_data %>%
select(product, lon, lat) %>%
unique()
# 
# ## For testing the nest/map pipeline
# # df <- site_pixels %>%
# #   filter(site == "Lamberts Bay") %>%
# #   select(-site)
# 
match_func <- function(df){
  df <- df %>%
    dplyr::rename(lon_site = lon, lat_site = lat)
  OISST_index <- OISST_prod[as.vector(knnx.index(as.matrix(OISST_prod[,c("lon", "lat")]),
                                                 as.matrix(df[,c("lon_site", "lat_site")]), k = 1)),] %>%
    cbind(., df)
  CMC_index <- CMC_prod[as.vector(knnx.index(as.matrix(CMC_prod[,c("lon", "lat")]),
                                             as.matrix(df[,c("lon_site", "lat_site")]), k = 1)),] %>%
    cbind(., df)
  res <- rbind(OISST_index, CMC_index)
  return(res)
}

# # Find the nearest pixels to each spot along the transect
# # NB: SOme pixels are used more thanonce in a transect as the spacing isn't quite larger enough between transect
# # points to not fall inside of the same 25 KM pixel
pixel_match <- site_pixels %>%
  group_by(site) %>%
  group_modify(~match_func(.x))
